Sparse associative memories

### 2014-06-23 Articles/article.tex
...

	probabilities for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective cluster : $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$

>>>>

	probability for none of the vertices in any erased cluster, excepting the correct ones, to achieve the maximum in their respective cluster : $\left(1 - d^	{a(c-c_e)}\right)^{c_e(l-a)}$
